---
title: "Adding icons to R Markdown using the `Fontawesome` package -- a short tutorial"
author: "Mark Bounthavong"
date: "2022-11-29"
output: html_document
---


### Font Awesome
[Font Awesome](https://github.com/rstudio/fontawesome) is an R package that allows you to insert an icon onto an R Markdown document. I came across this resource when I was learning how to build a curriculum vitae (CV) using `pagedown`, a convenient R package that allows you to build customized CV. 


### Instructions
Make sure to install the `fontawesome` package in R by typing: `install.packages("fontawesome")`.

Then load the library with `fontawesome`: `library("fontawesome")`

If you want to generate a list of icons available with fontawesome, type `fa_metadata()` in the Console. This will create a list of all known icons that you can use. However, this will be a very long list. An alternative way to find icons is to go to the `fontawesome.com` website [link](https://fontawesome.com/v5/icons/r-project?s=solid&f=brands). Note: Not all icons are available; you may need to wait for an update to the `fontawesome` package. 

Let's load the library `fontawesome` and add some icons to our in-line text. 
```{r load_packages, message = FALSE, warning = FALSE, include = TRUE} 
library("fontawesome")
```

Once the `fontawesome` package has been loaded, you can begin to add cool fonts into your R Markdown text. 

For example, "I would like to discuss how education `r fa("fas fa-book", fill = "black")` affects our responders."

To insert the book icon, I typed the following code after education: 

```{r, eval = FALSE}
`r fa("fas fa-book", fill = "black")`
```

This will generate a black book icon. I can change the color to red by replacing `black` with `red`.

Here is the red book icon: `r fa("fas fa-book", fill = "red")`


Another example: "My friends and I used to use Teamspeak `r fa("fab fa-teamspeak", fill = "black")` when we played World of Warcraft. Now, we use Discord `r fa("fab fa-discord", fill = "black")`."

I included the following code chunk into the text:

```{r, eval = FALSE}
Teamspeak icon: `r fa("fas fa-teamspeak", fill = "black")`
Discord icon: `r fa("fas fa-discord", fill = "black")`
```

To make the icon bigger, you will need to include the `height` option in the code chunk: 

"Here is a bigger icon (x2) for Discord `r fa("fab fa-discord", fill = "black", height = "2em")`"

"Here is a bigger icon (x3) for Discord `r fa("fab fa-discord", fill = "black", height = "3em")`"

### Summary
This is a new discovery, and I will likely update this tutorial as I learn more. Consider this a work in progress.


### References
[Font Awesome PDF documentation](https://cran.r-project.org/web/packages/fontawesome/fontawesome.pdf)

[Font awesome developer site](https://rstudio.github.io/fontawesome/)
